Lab2

### 2021-08-03 src/data/DataCleaning.Rmd
added age and income data.

#drop na and duplicates
d <- d %>% drop_na()
d <- unique(d)

#merge county policies to d
# d_openings$strict <- d_openings$Closed.bars.x2 != "0"

# d_openings$State.Postal.Code <- d_openings$State.Abbreviation
# d <- merge(x = d, y = d_openings[ , c("State.Postal.Code", "strict")], by = "State.Postal.Code", all.x = TRUE)
```

@@

```{r}
library(dplyr)
df = df %>% mutate(D=gsub("\\..*","",A))

              A    B   C    D
   awer.ttp.net Code 554 awer
   abcd.ttp.net Code 747 abcd
   asdf.ttp.net Part 554 asdf
    xyz.ttp.net Part 747  xyz

    names(df) <- substring(names(df), 4)
```

```{r clean dp03 data, echo=FALSE}
# filters by date/state
econ <- dp03_econ %>%
  rename(fips = GEO_ID, unemp_rate = DP03_0009PE) %>%
  select(fips, unemp_rate) %>%
  mutate(
    fips = substring(fips, 10)
  )

@@

# Clean up
```{r remove interim dataframes}
# remove dataframes
rm(d_covid, d_trips, d_openings)
rm(dp03_econ, dp05_age, density, s1901_income, urb_rur_h2)

>>>>

#drop na and duplicates
d <- d %>% drop_na()
d <- unique(d)
```

@@

```{r clean dp03 data, echo=FALSE}
# filters by date/state
econ <- dp03_econ %>%
  rename(fips = GEO_ID, unemp_rate = DP03_0009PE) %>%
  select(fips, unemp_rate) %>%
  mutate(
    fips = substring(fips, 10),
    unemp_rate = as.double(unemp_rate)
  )

@@

```{r clean dp03 data, echo=FALSE}
# filters by date/state
age <- dp05_age %>%
  rename(fips = GEO_ID,
         female = DP05_0003PE, 
         pct_lt5 = DP05_0005PE, 
         pct_5to9 = DP05_0006PE, 
         pct_10to14 = DP05_0007PE, 
         pct_15to19 = DP05_0008PE, 
         pct_20to24 = DP05_0009PE, 
         pct_25to34 = DP05_0010PE, 
         pct_35to44 = DP05_0011PE, 
         pct_45to54 = DP05_0012PE
) %>% rowwise() %>%
  mutate(
    fips = substring(fips, 10),
    female = as.double(female), 
    pct_lt5 = as.double(pct_lt5), 
    pct_5to9 = as.double(pct_5to9), 
    pct_10to14 = as.double(pct_10to14), 
    pct_15to19 = as.double(pct_15to19), 
    pct_20to24 = as.double(pct_20to24), 
    pct_25to34 = as.double(pct_25to34), 
    pct_35to44 = as.double(pct_35to44), 
    pct_45to54 = as.double(pct_45to54),
    pct_gt55 = 100 - sum(c(pct_lt5, pct_5to9, pct_10to14, pct_15to19, pct_20to24, pct_25to34, pct_35to44, pct_45to54)),
    pct_lt19 = sum(c(pct_lt5, pct_5to9, pct_10to14, pct_15to19)),
    pct_10to54 = 100 - pct_gt55 - pct_lt19
    ) %>%
  select(fips, pct_lt19, pct_10to14, pct_gt55)

# merge into main dataframe
d <- merge(x = age, y = d, by = c("fips"))
```

```{r clean s1901 data, echo=FALSE}
# filters by date/state
income <- s1901_income %>%
  rename(fips = GEO_ID,
  median_income = S1901_C01_012E,  
  pct_50to75k = S1901_C01_007E, 
  pct_75to100k = S1901_C01_008E, 
  pct_100to150k = S1901_C01_009E, 
  pct_150to200k = S1901_C01_010E, 
  pct_gt200k = S1901_C01_011E
) %>% rowwise() %>%
  mutate(
    fips = substring(fips, 10),
    median_income = as.double(median_income), 
    pct_50to75k = as.double(pct_50to75k), 
    pct_75to100k = as.double(pct_75to100k), 
    pct_100to150k = as.double(pct_100to150k), 
    pct_150to200k = as.double(pct_150to200k), 
    pct_over_us_median = sum(c(pct_50to75k, pct_75to100k, pct_100to150k, pct_150to200k))) %>%
  select(fips, median_income, pct_over_us_median)

# merge into main dataframe
d <- merge(x = income, y = d, by = c("fips"))
```

# Clean up
```{r remove interim dataframes}
# remove dataframes
rm(d_covid, d_trips, d_openings)
rm(dp03_econ, dp05_age, density, s1901_income, urb_rur_h2, econ, income, age)
